% !TeX root = ../main.tex


\begin{achievelist}
\item \textbf{JIANG J}, ZHENG N. MixPHM: Redundancy-aware parameter-efficient tuning for low-resource visual question answering[C]. IEEE Conference on Computer Vision and Pattern Recognition. IEEE, 2023: 24203-24213. 
(已录用)

\item \textbf{JIANG J}, LIU Z, ZHENG N. Correlation Information Bottleneck: Towards adapting pretrained multimodal models for robust visual question answering[J]. International Journal of Computer Vision, 2023. 
(在审)

\item \textbf{JIANG J}, LIU Z, ZHENG N. LiVLR: A lightweight visual-linguistic reasoning framework for video question answering[J]. IEEE Transactions on Multimedia, 2022. 
(已录用)
% (最有学术影响力的国际期刊，已录用, EI: 20222812350777)

\item \textbf{JIANG J}, LIU Z, LIU Y, et al. X-GGM: Graph generative modeling for out-of-distribution generalization in visual question answering[C]. ACM International Conference on Multimedia. ACM, 2021: 199-208. 
(EI: 20214711199999)

\item \textbf{JIANG J}, NAN Z, CHEN H, et al. Predicting short-term next-active-object through visual attention and hand position[J]. Neurocomputing, 2021, 433: 212-222. 
(SCI: 000624310100002)
% , EI: 20210509869900

\item \textbf{JIANG J}, XUE P, CHEN S, et al. Line feature based extrinsic calibration of LiDAR and camera[C]. IEEE International Conference on Vehicular Electronics and Safety. IEEE, 2018: 1-6. 
(EI: 20184906215158) 

\item CHEN H, \textbf{JIANG J}, ZHENG N. Learning to Infer Unseen Single- / Multi-Aattribute-Object Compositions with Graph Networks[J]. IEEE Transactions on Pattern Analysis and Machine Intelligence, 2023. 
(已录用)

\item NAN Z, \textbf{JIANG J}, GAO X, et al. Predicting task-driven attention via integrating bottom-up stimulus and top-down guidance[J]. IEEE Transactions on Image Processing, 2021, 30: 8293-8305. 
(SCI: 000702559700007)
% , EI: 20213910957531

\item NAN Z, PENG J, \textbf{JIANG J}, et al. A joint object detection and semantic segmentation model with cross-attention and inner-attention mechanisms[J]. Neurocomputing, 2021, 463: 212-225. 
(SCI: 000698041600018)

\end{achievelist}


% \begin{achievelist}
% \item LiVLR: A lightweight visual-linguistic reasoning framework for video question answering[J]. IEEE Transactions on Multimedia. 
% （一作）

% \item X-GGM: Graph generative modeling for out-of-distribution generalization in visual question answering[C]. ACM International Conference on Multimedia. 
% （一作）

% \item Correlation Information Bottleneck: Towards adapting pretrained multimodal models for robust visual question answering[J]. International Journal of Computer Vision. 
% （一作，在审）

% \item MixPHM: Redundancy-aware parameter-efficient tuning for low-resource visual question answering[C]. IEEE Conference on Computer Vision and Pattern Recognition. 
% （一作）

% \item Predicting short-term next-active-object through visual attention and hand position[J]. Neurocomputing. 
% （一作）

% \item Predicting task-driven attention via integrating bottom-up stimulus and top-down guidance[J]. IEEE Transactions on Image Processing. 
% （二作）

% % \item A joint object detection and semantic segmentation model with cross-attention and inner-attention mechanisms[J]. Neurocomputing. 

% \item Line feature based extrinsic calibration of LiDAR and camera[C]. IEEE International Conference on Vehicular Electronics and Safety. 
% （一作）
% \end{achievelist}


% \vspace{\baselineskip}
% {\color{red} 用于双盲评审的论文，只列出已发表的学术论文的篇名、发表刊物名称，必须隐去各类论文检索号、期号、卷号、页码；专利号；日期等。}

